---
title: "Motor Trend"
author: "laubolgo"
date: "23 de septiembre de 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Motor Trend Data and Libraries 
```{r, echo=TRUE}
library(ggplot2)
data(mtcars)
head(mtcars, n=3)
dim(mtcars)
mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$vs <- as.factor(mtcars$vs)
mtcars$am <- factor(mtcars$am)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
attach(mtcars)
```

## Exploratory Analysis

Exploratory Box plot compares Automatic and Manual transmission MPG. The graph leads us to believe that there is a significant increase in MPG when for vehicles with a manual transmission vs automatic.

```{r, echo=TRUE}
  boxplot(mpg ~ am, 
          xlab="Transmission Type (0 = Automatic, 1 = Manual)", 
          ylab="MPG",
          main="MPG by Transmission Type")
```

### Statistical Inference

T-Test transmission type and MPG

```{r, echo=TRUE}
testResults <- t.test(mpg ~ am)
testResults$p.value
```

The T-Test rejects the null hypothesis that the difference between transmission types is 0.
 
```{r, echo=TRUE}
testResults$estimate
```

The difference estimate between the 2 transmissions is 7.24494 MPG in favor of manual.

### Regression Analysis

Fit the full model of the data.

```{r, echo=TRUE}
fullModelFit <- lm(mpg ~ ., data = mtcars)
summary(fullModelFit)  # results hidden
summary(fullModelFit)$coeff  # results hidden
```

Since none of the coefficients have a p-value less than 0.05 we cannot conclude which variables are more statistically significant.

Backward selection to determine which variables are most statistically significant.

```{r, echo=TRUE}
stepFit <- step(fullModelFit)
summary(stepFit) # results hidden
summary(stepFit)$coeff # results hidden
```

### Residual and Diagnosis

```{r, echo=TRUE}
sum((abs(dfbetas(stepFit)))>1)
par(mfrow = c(2, 2))
plot(stepFit)
```

## Conclusion

There is a difference in MPG based on transmission type. A manual transmission will have a slight MPG boost. However, it seems that weight, horsepower, & number of cylinders are more statistically significant when determining MPG.

This model better explains the correlation of transmission on MPG values. It explains that 83.99% of the variance seen in the data set and there by conclude that on average, manual transmission cars have 2.084 MPGs more than automatic transmission cars holding the other variables constant.




